msprime 1.0: an efficient and extensible coalescent simulation framework

### 2020-02-26 paper.tex
Citations for pyvolve.

Thus, development of \msprime\ is not completed and much remains
to be done. For example, one key aim of the 1.0 series is to
improve the mutation models supported which are limited to
simple infinite-sites currently. The ability to simulate
sophisticated mutation models like Seq-Gen~\citep{rambaut1997seq}
and Dawg~\citep{cartwright2005dna} at the megasample scale would be
useful in many applications. Another key focus of development
will be [WHAT?]

>>>>

Thus, development of \msprime\ is not completed and much remains
to be done. For example, one key aim of the 1.0 series is to
improve the mutation models supported which are limited to
simple infinite-sites currently. The ability to simulate
sophisticated mutation models like Seq-Gen~\citep{rambaut1997seq},
Dawg~\citep{cartwright2005dna} and Pyvolve~\citep{spielman2015pyvolve} at the megasample scale would be
useful in many applications. Another key focus of development
will be [WHAT?]
